HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-17 hermes_paper/hermes_paper.tex
add m4 dataset results

>>>>

\subsection{Result for M4 weekly dataset}

\begin{table*}
  \caption{Results summary on the m4 weekly dataset. For each metric, the average on all our time series is computed. For approaches using neural network, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
    %\hline
  \end{tabular}
  }
\label{tab:metricresults}
\end{table*}
